Mixture-of-tastes Models for Representing Users with Diverse Interests

### 2018-01-18 paper/paper.tex
Start reformulatinnng model section.

@@

Within the classical matrix factorization framework, we experiment with two approaches to modelling taste mixtures. The first is the Projection-Mixture Factorization (\textbf{PM-F}) model. It extends the basic matrix factorization model by using linear projection layers on top of user latent vectors to model multiple tastes. In contrast, the Embedding-Mixture Factorization (\textbf{EM-F}) model directly embeds all the mixture parameters for each user. This makes it less parsimonious, but potentially more expressive.

>>>>

Within the classical matrix factorization framework, we experiment with two approaches to modelling taste mixtures. The first is the Embedding-Mixture Factorization (\textbf{EM-F}) model. In this model, a user is represented by two sets of $m$ $k$-dimensional latent vectors: one where the vectors correspond to their tastes, and one that describes how competent each taste is at describing a given item. When evaluating an item, the dot products of the second set of vectors with the item latent vector give the relative weights of each tastes from the first set that should be applied when evaluating the user's preference. Compared to a traditional factorization model, the EM-F model requires $2m$ as many parameters, giving it more expressive power at the expense of using more parameters.

The second factorization model we test is the Projection-Mixture Factorization (\textbf{PM-F}) model. It extends the basic matrix factorization model by using linear projection layers on top of user latent vectors to model multiple tastes: instead of embedding $m$ taste vectors and $m$ mixture vectors directly, we use $2m$ $k \times k$ projection matrices to project a single $k$-dimensional user item vector into $m$ taste and $m$ mixture vectors. These matrices are shared between all users, making the model substantially more parsimonious.

@@
